Switch equivalence for left-linear rewriting systems

### 2024-01-31 icalp/fusione.tex
summary

Rewriting systems over graphs are used in uncountably many setting for
representing the dynamics of software systems: the graph represents
the entities in the states and their relations, while rewriting steps,
modifying the graph, model computational steps which produce state
changes.

Rewriting over many kind of graphs is elegantly captured by the
so-called \emph{double pushout} (DPO) approach to rewriting. A
convenient fact is that DPO rewriting can be defined over adhesive
categories and their
variants~\cite{lack2005adhesive,ehrig2006weak}. Working in the
framework of adhesive categories allows one to devise the foundations
of a rewriting theory which can then be instantiated to the setting of
interest, avoiding to prove over and over similar ad-hoc results in
each specific context.

>>>>

Rewriting systems over graphs are used in uncountably many setting for
representing the dynamics of software systems: the graph serves to represent
the entities and their relations within states , while rewriting steps,
modifying the graph, model computational steps that results in
changes to the system state.

Rewriting over many kind of graphs is elegantly captured by the
so-called \emph{double pushout} (DPO) approach to rewriting. A
noteworthy advantage is that DPO rewriting can be formulated over
adhesive categories and their
variants~\cite{lack2005adhesive,ehrig2006weak}. Operating within the
framework of adhesive categories allows one to devise the foundations
of a rewriting theory which can be subsequently instantiated to the
context of interest, thus avoiding the need of repeatedly proving
similar ad-hoc results in for each specific setting.
